\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-05 paper/sp.tex
tabular output and how to use it

The linear model we use has a big limitation: Linear models are inflexible.
However, it has a great advantage over more general methods,
which is that it is easy to look inside
the linear model and check whether the dependencies represented there make sense.
One nice thing about the model is that the feature vector $x_n$ for star $n$
contains a set of photometry in magnitudes.
Linear combinations of these photometric measurements are like complex synthetic
magnitudes or colors.
Since the model was trained to deliver luminosities of stars given training data
of different metallicities and extinctions, the synthetic photometry developed
by the model should be, in some sense, metallicity- and extinction-independent
photometry for luminous red-giant stars!
In detail this synthetic magnitude is something like HOGG PUT EQUATION HERE AND
SAY SOMETHING ABOUT IT. HOGG: Maybe plot this synthetic photometry against dust
and metallicity.

@@

HOGG: How to get the data and how to use it, probabilistically.

@@

\software{} % This command is wack
The code used in this project is available from
\url{https://github.com/aceilers/spectroscopic_parallax}.
It is released under the MIT (HOGG CHECK) open-source software license.
This research additionally utilized:
\code{Astropy} (\citealt{astropy, astropy2}),
\code{IPython} (\citealt{ipython}),
\code{matplotlib} (\citealt{matplotlib}),
\code{numpy} (\citealt{numpy}), and
\code{scipy} (\citealt{scipy}).

\facilities{\sdssiv, \apogee, \apogee-2, \gaia, \zmass, \wise}

>>>>

The linear model we use has a big limitation: Linear models are inflexible.
However, it has a great advantage over more general methods,
which is that it is easy to look inside
the linear model and check whether the dependencies represented there make sense.
The feature vector $x_n$ for star $n$
contains a set of photometry in magnitudes.
Linear combinations of these photometric measurements are like complex synthetic
magnitudes or colors.
Since the model was trained to deliver luminosities of stars given training data
of different metallicities and extinctions, the synthetic photometry developed
by the model should be, in some sense, metallicity- and extinction-independent
photometry for luminous red-giant stars!
In detail this synthetic magnitude is something like HOGG PUT EQUATION HERE AND
SAY SOMETHING ABOUT IT. HOGG: Maybe plot this synthetic photometry against dust
and metallicity.

@@

In the end, this method produces a spectrophotometric parallax estimate $\sparallax_m$ for
every star $m$.
\tablename~\ref{tab:output} shows a snippet of this output, with the full output available
as an electronic data table associated with this \documentname.
In order to use this output with \gaia\ astrometry, we recommend joining the table to the
\gaia\ Catalog on the \zmass\ ID (name), as per the instructions at the \Gaia\ Archive (CITE).

In order to use these outputs in a probabilistic inference or forward model,
an investigator needs a noise (uncertainty) model.
The linear model permits straightforward propagation of uncertainty from the
feature inputs.
However, these propagated uncertainties clearly under-predict the scatter between
the spectrophotometric parallaxes $\sparallax_m$ and the \gaia\ astrometric
parallaxes $\gparallax_m$.
Our recommendation for an uncertainty model is HOGG WAT?

@@

\facilities{
\sdssiv(\apogee-2),
\gaia,
\zmass,
\wise}

\software{
\code{Astropy} \citep{astropy, astropy2},
\code{IPython} \citep{ipython},
\code{matplotlib} \citep{matplotlib},
\code{numpy} \citep{numpy},
\code{scipy} \citep{scipy}}
